%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1 }{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[6]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textbf{#5} & #6  \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingEight}[8]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textbf{#5} & #6  \\
      \textbf{\small#7} & \emph{\small #8} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[label={},leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[label={}]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Arkadeep Narayan Chaudhury}} & \underline{Email: \href{mailto:arkadeepnc@cmu.edu}{arkadeepnc@cmu.edu}} \\ 
  \href{https://arkadeepnc.github.io}{\texttt{https://arkadeepnc.github.io}} & Cell: +1 412-626-4231 \\
  \href{https://www.linkedin.com/in/arkadeepnc/}{LinkedIn}, \href{https://github.com/arkadeepnc}{GitHub} &4225 Newell-Simon Hall, 5000 Forbes Avenue\\ \href{https://www.researchgate.net/profile/Arkadeep_Chaudhury}{ResearchGate} &  Carnegie Mellon University, Pittsburgh, PA, ZIP: 15232\\

\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Carnegie Mellon University, Robotics Institute}{Pittsburg, PA}
      {MS + PhD in Robotics}{Aug. 2020 -- May 2024 (expected)} {}{}
      \vspace{-0.2 in}
      \resumeSubheading
      {Carnegie Mellon University, CIT}{Pittsburg, PA}
      {PhD in Mechanical Engineering}{Aug. 2018 -- Aug 2020 (transferred to the RI) } {}{}
      \vspace{-0.2 in}
    \resumeSubheading
      {Indian Institute of Science}{Bangalore, India}
      {Master of Science in Mechanical Engineering}{Aug. 2015 -- Dec. 2017} {}{}
       \vspace{-0.2 in}
    \resumeSubheading
      {Indian Institute of Engineering Science and Technology}{Shibpur, India}
      {Bachelor of Engineering in Mechanical Engineering}{Jul. 2011 -- May 2015} {}{}
       \vspace{-0.2 in}
  \resumeSubHeadingListEnd

% ---------------------------

\section{Research Experience}
\begin{description}
\item Neural 3D representations, 3D reconstruction, 3D sensing for small scenes, sensor fusion, active perception, design of low-level computer vision systems, robotic manipulation. 
\vspace{-0.1 in}
% \item[Sports:] Biking and badminton.s
\end{description}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Toyota Research Institute}{Los Altos, CA}
      {Research Scientist Intern}{ May. 2023 -- Aug. 2023}  {Team:}
          {ML @ TRI}
      \resumeItemListStart
        \resumeItem{Physically based 3D representations:}
          {Researched algorithms on physically based capture of 3D assets for robotics. Developed a robot mounted multi-flash stereo camera rig to capture multi-modal data from small objects in bounded scenes.}  {[Patent filed]}      
          \resumeItemListEnd
          
    \resumeSubheadingEight
      {Atkeson Lab, CMU RI}{Pittsburgh, PA}
      {Graduate Research Assistant}{ Nov. 2019 -- Present} {Advisor:}
          {\href{https://www.cs.cmu.edu/~cga/}{Prof. Christopher Atkeson} }{Thesis topic:} {Moving lights and cameras for better 3D vision}
      \resumeItemListStart
        \resumeItem{Moving cameras:}
          {Developed an ensemble of collocated vision, depth and touch sensors and a set of algorithms to visually servo robots to workspace goals and localize objects through vision and touch. \href{https://arkadeepnc.github.io/projects/collocated_vision_touch}{ICRA \& RA-L'22}}
          \resumeItem{Moving lights:}
          {Designed and implemented a robot workspace scale photometric stereo setup for object agnostic, surface texture, surface orientation, and surface deformation perception. \href{https://arkadeepnc.github.io/projects/active_workspace}{WACV'24} 
          \resumeItem{Moving lights and cameras:}
          {Designed and implemented a portable multi-flash stereo camera for appearance and geometry perception of small scenes.  }{\href{https://stereomfc.github.io}{Project}} }
        \resumeItemListEnd

    % \resumeSubheading
    %   {CI2CV Lab, CMU RI}{Pittsburgh, PA}
    %   {Graduate Research Assistant}{ July. 2019 -- Nov. 2019}  {Advisor:}
    %       {\href{https://www.adelaide.edu.au/directory/simon.lucey}{Prof. Simon Lucey}}
    %   \resumeItemListStart
    %     \resumeItem{Learning-Based Registration:}
    %       {Researched learning-based pose estimation algorithms -- insights on why it works, what are the open problems.: \href{https://www.overleaf.com/read/jsjhbmspsjjq}{Short report}.}        
    %       \resumeItemListEnd
    \resumeSubheading
      {Biorobotics Lab, CMU RI}{Pittsburgh, PA}
      {Graduate Research Assistant}{ Aug. 2018 - Jul. 2019}  {Advisor:}
          {\href{https://www.cs.cmu.edu/~./choset/bio.html}{Prof. Howie Choset}}
      \resumeItemListStart
        \resumeItem{Medical device prototype:}
          {Co-developed and prototyped a hand held soft tissue investigation device for low-cost tumor diagnosis. \href{https://www.researchgate.net/publication/333968217_Hand-held_stiffness_measurement_device_for_tissue_analysis}{Hamlyn '19}}
      \resumeItem{Non-rigid registration:}
          {Surveyed algorithms for human organ registration and proposed and implemented faster algorithms with comparable accuracy to handle larger volumes of data. \href{https://www.overleaf.com/read/ybdjnxzvtmwy}{Link}}
        
      \resumeItemListEnd
  \resumeSubheading
      {Robotics and Design Lab, IISc}{Bangalore, India}
      {Research Staff}{ Jan. 2018 - Jul. 2018}  {Advisor:}
          {\href{https://mecheng.iisc.ac.in/~asitava/}{Prof. Ashitava Ghosal}}
      \resumeItemListStart
        \resumeItem{Optimal Motion Planning:}
          {Derived optimal, polynomial time motion plans for snake-like robots in confined spaces such as endoscopes in GI tract, pipe inspection robots and in cluttered search and rescue scenarios. \href{https://www.sciencedirect.com/science/article/pii/S0010448518304135}{CAD}}
        
          \resumeItemListEnd
  \resumeSubheading
      {Robotics and Design Lab, IISc}{Bangalore, India}
      {Graduate Research Assistant}{ Jul. 2015 - Dec. 2017}  {Advisor:}
          {\href{https://mecheng.iisc.ac.in/~asitava/}{Prof. Ashitava Ghosal}}
      \resumeItemListStart
        \resumeItem{Design of Parallel Robots:}
          {Designed Monte Carlo simulations to model workspaces of parallel robots. Modeled the human 3-fingered grasp and proposed techniques for optimal design of parallel robots. \href{https://www.researchgate.net/publication/327670588_Kinematic_Design_and_Optimal_Synthesis_of_Parallel_Manipulators_Using_Monte_Carlo_Method}{Thesis}, \href{https://www.sciencedirect.com/science/article/abs/pii/S0094114X16303184}{MMT}, \href{https://asmedigitalcollection.asme.org/mechanismsrobotics/article-abstract/10/4/041003/366587/Workspace-of-Multifingered-Hands-Using-Monte-Carlo?redirectedFrom=fulltext}{JMR}. }
        
          \resumeItemListEnd
% \resumeSubheading
%       {Solid Mechanics Lab, IIEST}{ Kolkata, India}
%       {Undergraduate Researcher}{Jul. 2014 - Apr. 2015}  {Advisor:}
%           {\href{https://www.iiests.ac.in/IIEST/Faculty/mech-ddatta}{Prof. Debasis Datta}}
%       \resumeItemListStart
%         \resumeItem{Computational Design of Springs:}
%           {Formulated closed form expressions for design of springs of un-conventional shapes to estimate their stresses, natural frequencies, buckling loads etc. \href{https://www.sciencedirect.com/science/article/pii/S2288430016301385}{Link} }
       
%       \resumeItemListEnd
  \resumeSubHeadingListEnd

%-- Projects
\section{Selected Course Projects}
\resumeSubHeadingListStart
\resumeSubItem{Planning on Manifolds:}{ Devised algorithms for path planning of collaborative robot arms to manipulate ultra-sound probes on a human body phantom. This algorithm was lated used to research automatic femoral artery catheterization. [\href{https://drive.google.com/file/d/1MkV6iC-KX0RYu9jkbsk1KcqY43s-AwOh/view?usp=sharing}{Video}] }
\resumeSubItem{SLAM for Legged Robots:} {Used GTSAM and OpenCV to co-develop a framework for visual state estimation in legged robots using their gait information. [\href{https://drive.google.com/file/d/1IkJY9AmxFcWgnp1tYTT9mZcW5MmxTrkQ/view?usp=sharing}{Report}]}
\resumeSubHeadingListEnd


%-----------Publications-----------------
\section{Publications. \small{[\href{https://scholar.google.com/citations?user=rZ58Bf8AAAAJ&hl=en}{Google Scholar Page}}]}
  \resumeSubHeadingListStart

  \resumeSubItem{[1]}
      { \textbf{Chaudhury, A. N.}, Keselman, L.  \& Atkeson, C. (2022) ``Controlled illumination for perception and manipulation of Lambertian objects'' \emph{Proc. of the WACV `24} \href{https://arkadeepnc.github.io/projects/active_workspace/index.html}{Link}}
  
    \resumeSubItem{[2]}
      { \textbf{Chaudhury, A. N.}, Man, T.  Yuan, W. \& Atkeson, C. (2022) ``Using Collocated Vision and Tactile Sensors for Visual Servoing and Localization.'' \emph{IEEE RA-L 2022} \href{https://arkadeepnc.github.io/projects/collocated_vision_touch/index.html}{Link}}
      
    \resumeSubItem{[3]}
      {Ashwin K.P.*, \textbf{Chaudhury A.N.*}, and Ashitava Ghosal. (2020) ``Efficient representation of ducts and cluttered spaces for realistic motion planning of hyper-redundant robots through confined paths.''J. Computer-Aided Design, 119, 102777. \href{https://www.sciencedirect.com/science/article/pii/S0010448518304135}{Link}}
      
    \resumeSubItem{[4]}
      { \textbf{Chaudhury, A. N.}, \& Ghosal, A. (2017). ``Optimum design of multi-degree-of-freedom closed-loop mechanisms and parallel manipulators for a prescribed workspace using Monte Carlo method''. Mechanism and Machine Theory, 118, 115-138.  \href{https://www.sciencedirect.com/science/article/abs/pii/S0094114X16303184}{Link}}
      
  \resumeSubItem{[5]}
  {\textbf{Chaudhury, A. N.}, \& Ghosal, A. (2018). ``Workspace of Multi-fingered Hands Using Monte Carlo Method''. Journal of Mechanisms and Robotics, 10(4), 041003. \href{https://asmedigitalcollection.asme.org/mechanismsrobotics/article-abstract/10/4/041003/366587/Workspace-of-Multifingered-Hands-Using-Monte-Carlo?redirectedFrom=fulltext}{ Link}}
  
  \resumeSubItem{[6]}
  {\textbf{Chaudhury, A. N.}, \& Datta, D. (2017). ``Analysis of prismatic springs of non-circular coil shape and non-prismatic springs of circular coil shape by analytical and finite element methods''. Journal of Computational Design and Engineering, 4(3), 178-191.
\href{https://www.sciencedirect.com/science/article/pii/S2288430016301385}{Link}}
\resumeSubHeadingListEnd

%-----------------------

\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Programming Languages:}      {Python, C++, CUDA, Cython }
    \resumeSubItem{Robot platforms:}       {Universal Robots UR5, Franka Emika FR3, XArm-7}
    \resumeSubItem{Computing Environments:} {Linux [Ubuntu]}
    \resumeSubItem{Machine Learning Toolboxes:} {PyTorch, TensorFlow, SciKit-Learn}
    \resumeSubItem{Software Libraries:}{ROS, OpenCV, PCL, GTSAM}
    \resumeSubItem{Languages:}  {English (full proficiency), Bengali (native proficiency) and Hindi (bi-lingual proficiency)}
\resumeSubHeadingListEnd
%----------

\section{Relevant Courses}
  \resumeSubHeadingListStart
    \resumeSubItem{At CMU:}      {Computer Vision, Geometric Methods in Computer Vision, Advanced Nonlinear Control Theory, Robot Mapping and Localization, Linear Systems, Statistical Techniques in Robotics, Deep Reinforcement Learning, Machine Learning}
    \resumeSubItem{At IISc:} 
    {Robotics (Kinematics, Dynamics and Control), Numerical Linear Algebra, Geometric Modelling, Linear and Non-Linear Optimization, }
\resumeSubHeadingListEnd

%---
\section{Awards}
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		DST-SERB Overseas PhD fellowship (Govt. of India) [Declined] & 08/2018 -- 08/2023 \\
		Graduate Research Fellowship (CMU) & 08/2018 -- 08/2019 \\
		DST Graduate Scholarship (Govt. of India) & 08/2015 -- 12/2017\\		
\end{tabular*}

%-----------------



%-------------

\section{References}
\begin{description}
  \item[\href{https://www.cs.cmu.edu/~cga/}{Prof. Christopher G. Atkeson }] Professor, CMU, \href{mailto:cga@cmu.edu}{cga@cmu.edu} [advisor]
  \vspace{-0.1 in}
  % \item [Dr. Simon Lucey] Associate Research Professor, CMU, \href{mailto:slucey@cmu.edu}{slucey@cmu.edu}
  % \vspace{-0.1 in}
  \item[\href{https://mecheng.iisc.ac.in/~asitava/}{Prof. Ashitava Ghosal}] Professor, IISc Bangalore.  \href{mailto:asitava@iisc.ac.in}{asitava@iisc.ac.in} [ex. advisor]
  \vspace{-0.1 in}
  \item[\href{https://www.linkedin.com/in/igor-vasiljevic-9ba0a951/}{Dr. Igor Vasiljevic
}] Research Scientist, Toyota Research Inst., \href{mailto:igor.vasiljevic@tri.global}{igor.vasiljevic@tri.global} [Internship Mentor]
  \end{description}
  % More referees are available upon request.Igor Vasiljevic <igor.vasiljevic@tri.global>,
  
%-------------------------------------------
\end{document}

